LEMONADE: Leveraging Modern Automated Deduction for Program Synthesis\\ \vspace{0.5cm} \large{WWTF ICT 2022}

### 2022-04-11 WWTF/main.tex
asdf

  Program synthesis is a long-standing problem that crosses many areas of computer science and mathematics.
  Program synthesis holds the promise to  increase the reliability of software systems (because the synthesized program are correct by construction) and for increasing programmer productivity by enabling programmers to focus on high-level ideas instead of low-level details.

@@

%The complexity of modern software systems, including in particular, \emph{safety-critical systems}, continues to grow.
Traditionally quality assurance techniques rely on first building the desired system and then testing/verifying the system.
%, which may become costly or even impossible for sufficiently complex systems.
In contrast, \emph{correct-by-construction} approaches seek to develop a product that continues to be correct, from the initial design to the final product.
Advances in deductive synthesis promise to increase the applicability of the correct-by-construction approach, leading to higher reliability in software development.

Automated theorem proving has made impressive progress in recent years, demonstrated in yearly solver competitions.
We will submit our benchmarks to these competitions in order to interest solver developers in improving their tools wrt to the specific needs of deductive synthesis.
%(formulas with quantifier alternation, support for induction, etc.).

>>>>

  Program synthesis is a long-standing problem that crosses many areas of computer science and mathematics.
  Program synthesis holds the promise to  increase the reliability of software systems (because the synthesized program are correct by construction) and to increase programmer productivity by enabling programmers to focus on high-level ideas instead of low-level details.

@@

%The complexity of modern software systems, including in particular, \emph{safety-critical systems}, continues to grow.
Traditionally quality assurance techniques rely on first building the desired system and then testing/verifying the system.
%, which may become costly or even impossible for sufficiently complex systems.
In contrast, \emph{correct-by-construction} approaches seek to develop a system that continues to be correct, from the initial design to the final product.
Advances in deductive synthesis promise to increase the applicability of the correct-by-construction approach, leading to higher reliability in software development.

Automated theorem proving has made impressive progress in recent years, demonstrated in yearly solver competitions.
We will submit our benchmarks to these competitions in order to interest solver developers in improving their tools wrt the specific needs of deductive synthesis.
%(formulas with quantifier alternation, support for induction, etc.).
